Supporting Information

### 2022-03-08 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
Edits on text

#Read data
networks <- read_csv("../Data/Csv/data_for_motifs_analysis_1.csv")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020) without considering singletones. This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")

@@

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

@@

e.clust_5 <- readRDS("../Data/RData/e.clust_5.rds")

@@

# We use "darkgrey" to color some species
final_d_1 <- read.csv("../Data/Csv/data_for_motifs_analysis_1.csv")

>>>>

#Read data
networks <- read_csv("../../Data/Csv/data_for_motifs_analysis_1.csv")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020) without considering singletones. This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")

@@

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("../../Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("../../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

@@

e.clust_5 <- readRDS("../../Data/RData/e.clust_5.rds")

@@

# We use "darkgrey" to color some species
final_d_1 <- read.csv("../../Data/Csv/data_for_motifs_analysis_1.csv")
